\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{hyperref}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Checking the OpenLCB Datagram Transport Protocol}
\author{The OpenLCB Group}
%\date{}                                         % Activate to display a given date or no date

\begin{document}
\maketitle


\section{Introduction}

This note documents the procedure for checking an OpenLCB implementation against the 
\href{https://nbviewer.org/github/openlcb/documents/blob/master/standards/DatagramTransportS.pdf}{Datagram Transport Standard}.

The checks are traceable to specific sections of the Standard.

The checking assumes that the Device Being Checked (DBC) is being exercised by other
nodes on the message network, 
e.g. is responding to enquiries from other parts of the message network.

\subsection{Required Equipment}

See the separate ``Installing the OpenLCB Checker Software" document for initial installation 
and set up of the checker program.

If a direct CAN connection will be used,
a supported USB-CAN adapter
    \footnote{See ``Installing the OpenLCB Checker Software"}
is required. 
Connect the adapter to the DBC using a single UTP cable and connect two CAN terminators.

Provide power to the DBC using its recommended method.

\section{Set Up}
The following steps need to be done once to configure the checker program:.
\begin{enumerate}
\item Start the checker configuration program. 
\item Select ``Set Up".
\item Get the Node ID from the DBC\footnote{Where do we require this to be marked on a node?} 
\item Enter that Node ID into the program.
\item Configure the checker program for the USB-CAN adapter's device address
        or the TCP hostname and port.
\item Quit the checker program and reply ``Y" to "Save configuration?" when prompted.
\end{enumerate}

The following steps need to be done at the start of each checking session.
\begin{enumerate}
\item Check that the DBC is ready for operation.
\item Start the checker program.
\end{enumerate}

\section{Datagram Transport Procedure}

Select ``Datagram checking" in the checkere program, 
then select each section below in turn.  Follow the prompts
for when to check outputs against the node documentation.

Note that this process is unable to check datagrams from the DBC to the checker.
There is no standard way to elicit those.  They will be checked as part of the 
Memory Configuration Protocol checking, if applicable.

A node which does not self-identify in PIP that it supports
datagram transfer will be deemed to have passed these checks.
\footnote{Using the -p option or setting the checkpip default value False will skip this check.}

\subsection{Datagram Reception}

This checks the messages in Standard sections 4.1 and 4.2 or 4.3, 
including the error code constraints in Standard section 4.3.1
\footnote{This section references the Message Transport Standard, 
section 3.5.5}
and the interactions in sections 6.1 or 6.2.

The checker will send a datagram to the DBC. The DBC in turn will 
either accept the datagram (sections 4.2 and 6.1) or 
reject it (sections 4.3 and 6.2). Either response is acceptable.

This section's checks cover:

\begin{enumerate}
\item If the datagram is accepted,
    \begin{enumerate}
    \item That the Datagram OK message is received,
    \item That the Datagram OK message has proper source and destination node IDs, 
    \item that the Datagram OK message contains exactly 1 byte of flags,
    \item that the 0x70 bits of the flags are zeros.
    \end{enumerate}
\item if the datagram is rejected, 
    \begin{enumerate}
    \item That the Datagram Rejected message is received,
    \item That the Datagram Rejected message has proper source and destination node IDs, 
    \item that the Datagram Rejected message contains at least two bytes of error code,
    \item that the 0xF000 bits of the error code are either 0x1000 or 0x2000,
    \item that the 0x0F00 bits of the error code are zeros.
    \end{enumerate}
\end{enumerate}

This process is repeated for datagrams of length 1, 10 and 72 bytes to exercise the full
range of datagram framing.


\end{document}  
