\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{hyperref}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{OpenLCB test plan for the Memory Configuration Standard}
\author{The OpenLCB Group}
%\date{}                                         % Activate to display a given date or no date

\begin{document}
\maketitle


\section{Introduction}

This note documents the procedure for testing an OpenLCB implementation against the
\href{https://nbviewer.org/github/openlcb/documents/blob/master/standards/MemoryConfigurationS.pdf}
    {Memory Configuration Standard}.

The tests are traceable to specific sections of the Standard.

The testing assumes that the Device Under Test (DUT) is being exercised by other
nodes on the message network, 
e.g. is responding to enquiries from other parts of the message network.

\section{Required Equipment}

See the separate ``Installing the OpenLCB Test Software" document for initial installation 
and set up of the test program.

If a direct CAN connection will be used,
a supported USB-CAN adapter
    \footnote{See ``Installing the OpenLCB Test Software"}
is required. 
Connect the adapter to the DUT using a single UTP cable and connect two CAN terminators.

Provide power to the DUT using its recommended method.

\section{Set Up}
The following steps need to be done once to configure the test program:.
\begin{enumerate}
\item Start the test configuration program. 
\item Select ``Set Up DUT".
\item Get the Node ID from the DUT\footnote{Where do we require this to be marked on a node?} 
\item Enter that Node ID into the program.
\item Configure the test program for the USB-CAN adapter's device address
        or the TCP hostname and port.
\item Quit the test program and reply ``Y" to "Save configuration?" when prompted.
\end{enumerate}

The following steps need to be done at the start of each testing session.
\begin{enumerate}
\item Check that the DUT is ready for operation.
\item Start the test program.
\end{enumerate}

\section{Memory Configuration Procedure}

Select ``Memory testing" in the test program, 
then select each section below in turn.  Follow the prompts
for when to reset/restart the node and when to check 
outputs against the node documentation.

A node which does not self-identify in PIP that it supports
Memory Configuration will be deemed to have passed these tests.
\footnote{Using the -p option or setting the checkpip default value False will skip this check.}

This plan does not check:
\begin{enumerate}
\item Stream-based memory configuration operations
\item Writes to configuration memory.  THere's no generally-compatible way to do that.
You can't even assume that a read / write / read sequence will return you to the original
state, because nodes may react when information is written to them.
\item The Reinitialize/Factory Reset Command and the Get Unique ID Command and reply
because these permanently change the state of the node under test.
\end{enumerate}

\subsection{Configuration Options testing}

This section tests the messages and interaction in Standard sections 4.13 and 4.14.

The tester sends a Get Configuration Options Command datagram.  It then checks:
\begin{enumerate}
\item That the datagram reply is received.
\item That a Get Configurations Options Reply datagram is received,
\item The reply datagram i sat least six bytes long,
\item That the reserved bits in bytes 2, 3 and 4 are zero.
\end{enumerate}

\subsection{Address Space Information testing}

This section tests the messages and interaction in Standard sections 4.15 and 4.16.

For each of the required\footnote{See section 4.2}
0xFF, 0xFE and 0xFD memory spaces, the
tester sends a Get Configuration Options Command datagram.  It then checks:
\begin{enumerate}
\item That the datagram reply is received.
\item That a Get Address Space Information Reply datagram is received,
\item The reply datagram i sat least eight bytes long,
\item That the reply datagram refers to the same memory space as the request,
\item That the reply datagram shows the space is present,
\item That the reserved bits in byte 7 are zero.
\end{enumerate}

\subsection{Read Operations testing}

This section tests the messages and interaction in Standard sections 4.4 and 4.5.

The tester sends Read Commands to space 0XFD, the memory configuration space.

\begin{enumerate}
\item A read of 64 bytes from address 0,
\item A read of 2 bytes from address 0,
\item A read of 64 bytes from address (Space Length - 4), which should return four bytes.
\end{enumerate}

Each of these are done once with the address space in byte 1 
and once with the address space in byte 6.

For each, the tester checks:
\begin{enumerate}
\item The datagram reply has the Reply Pending bit set,
\item The reply datagram is long enough to be checked,
\item It's a Read Reply datagram,
\item The error bit is not set,
\item The space matches (in either form),
\item The starting address matches,
\item The right number of data bytes are returned.
\end{enumerate}

\subsection{Lock/Reserve testing}

This section tests the messages and interaction in Standard section 4.17 and 4.18.

The tester requests that the node be reset/restarted then 

\begin{enumerate}
\item Sends a Lock/Reserve Command with node id A
    and checks that a Lock/Reserve Reply is received with contents zero.
\item Sends a Lock/Reserve Command with node id B
    and checks that a Lock/Reserve Reply is received with contents A.
\item Sends a Lock/Reserve Command with node id B
    and checks that a Lock/Reserve Reply is received with contents A.
\item Sends a Lock/Reserve Command with zero 
    and checks that a Lock/Reserve Reply is received with contents A.
\item Sends a Lock/Reserve Command with node id B
    and checks that a Lock/Reserve Reply is received with contents zero.
\item Sends a Lock/Reserve Command with node id A
    and checks that a Lock/Reserve Reply is received with contents B.
\item Sends a Lock/Reserve Command with node id A
    and checks that a Lock/Reserve Reply is received with contents B.
\item Sends a Lock/Reserve Command with zero 
    and checks that a Lock/Reserve Reply is received with contents B.
\item Sends a Lock/Reserve Command with zero 
    and checks that a Lock/Reserve Reply is received with contents zero.

\end{enumerate}

\subsection{Reset/Reboot testing}

This section tests the message and interaction in Standard section 4.24 Reset/Reboot Command.

The tester sends a Reset/Reboot Command and then checks that a Node Initialization 
Complete message is received to indicate a reboot.  This may or may not have been
preceded by a Datagram Received OK response.

\end{document}  
